---
title       : Fuel consumption predictor
subtitle    : Project for the Developing Data Products Course
author      : alemorale
job         : Coursera data science specialization
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
knit        : slidify::knit2slides
---

## The shiny app - a fuel consumption predictor

The shiny app predicts the fuel consumption of a car with the following properties:

1. Weight
2. Cylinders
3. Horsepower

The algorithm, using the most advance statistical modeling techniques, is able to predict the mileage of a car, given that the weight, number of cylinders and horsepower of the car are known.


We are able to deploy our algorithm to the mtcars dataset to make predictions about fuel consumption for a car of given characteristics.


--- .class #id 

## The mtcars dataset

As we can observe, the dataset has several variables which the algoritm does not use in the prediction, we restrict our analysis to the most important variables controlling mileage, namely: weight, cylinders and horsepower.


```{r}
data(mtcars)
head(mtcars)
```

--- .class #id
## The prediction algorithm

The prediction algorithm is based on a standard linear regression model of the data in the mtcars dataset using the weight, cylinders and horsepower variables of the dataset.

```{r,echo=TRUE}
model <- lm(mpg ~ wt + cyl + hp, data = mtcars)
```

Given new data for a given by the user, for instance:
```{r}
weight <- 3
cylinders <- 6
horsepower <- 200
```

--- .class #id 

## Predictions

We are able to succesfully predict fuel consumption!

```{r}
predict(model,newdata=data.frame(wt=weight,cyl=cylinders,hp=horsepower))
```




As a reference, we provide the link to the shiny app: https://alemorales.shinyapps.io/project/


